TODO * learn how to use reCAPTCHA
TODO * make yearAgo in usersReviews dynamic 
TODO * ADD loading functionality in usersReviews .
TODO * add loading in product screen when getting the product form the backend
TODO * find a better way to handle recommend product.
TODO * make nutrition in database less complex
TODO * deal with the following problem if the user open more than one product in different pages or different review screen.
TODO * make update review temporary maybe for 30 minutes.
TODO * fix: reviews.reviews.map((review, index), in userReview
TODO * fix: images in product's reviews 
TODO * const userGoal = userInfo.goal || "Build Muscle"; try to find a better way to handle it. in Reviewing comp
TODO * const isVerifiedBuyer = false; modify it when adding VerifiedBuyer functionality in userModal
TODO * when click on write review don't open new window.
TODO * when closing the website learn how to clear local storage;
TODO * learn what's the difference between map and react.Children.map
TODO * fix the grip cursor in storeSectionSlider
TODO * try to find out how calling the following urls in StoreScreen:
         http://localhost:3000/store 
         http://localhost:3000/cdn-cgi/images/trace/jschal/js/transparent.gif?ray=6299ae5b19c4fd01 
TODO *  when the user refresh the page changeforgotten don't let the user visit the page again. 
TODO * fix recommend comp when the page less than 750px
TODO * ADD loading icon when the user report and we processing the report request from the backend
TODO * add redirecting functionality when the user login. i mean show the user last page before the user move to logging screen.
TODO * change reveiwModal.js name to reviewModal.js
TODO * when the user moves to another screen show him/her the beginning of the page.
TODO * when the user reviewed show him/her the review.
TODO * change swiper-pagination-bullet in homeScreen like the one in MuscleAndStrung
TODO * ADD the name of the product in the ReviewScreen.
TODO * fix  LoginDialog's move functionality 
TODO * read about the following warning 
       Mongoose: `findOneAndUpdate()` and `findOneAndDelete()` without the `useFindAndModify` option set to false are deprecated. See: https://mongoosejs.com/docs/deprecations.html#findandmodify
      (Use `node --trace-deprecation ...` to show where the warning was created)
TODO *   src="/images/user-login.png" make it dynamic (bring the image form the backend)
TODO * create new backend route for helpful functionality to make it faster, combine user update and review update in one update.
TODO * improve extra info filed in add product. for example let the user add more image or video and show him sampl.
TODO * improve extraInfo input in admin page, like let the user enter is many p he want or images,
       video, and it is in different page, and off course title.
TODO * try not add all the products when view more just append the new products.
TODO * try to close CountrySelector in cart screen when onBlur.
      <div
      style={{ minHeight: " 194px", zIndex: 3 }}
      tabIndex={0}
      onBlur={() => setIsOpen(false)}
    >
      <SodSelect
        id="SodSelect"
        title="Country"
        onClick={() => setIsOpen(!isOpen)}
        isOpen={isOpen}
      >
      ......
TODO * try to change the position of CountrySelector when it is out of the screen.
TODO * learning how to create more than one document in do it in add cartItem
TODO * improve cart add and get backend interaction.
TODO * fix "don't let the user select pick favor after select a favor"
TODO * improve "Home store/brans/MuscleTech" in TitleBlock component.
TODO * improve the style in storeSectionSlider the next and prev buttons
TODO * update the data of storeSectionSlider in brandScreen.
TODO clean up productModal.js
TODO learn how to delete document after sometime and apply it
      to deal modal when the expired date comes.
TODO clean up the following code (we don't need it anymore):
    useEffect(() => {
        dispatch(getPathName(props.location.pathname));
      }, [dispatch, props.location.pathname]);
TODO refactor the following code () make it as utilities:
    {
    //  
    //     error.response && error.response.data.message
    //       ? error.response.data.message
    //       : error.message,
    // name it as errorFromBackend(error)