TODO (not important) make NavBlock dynamic  
TODO (not important) fix cursors style in login popup window.
TODO (not important) clean up Modal comp.
TODO (not important) move HomeScreen and StoreScreen and LoginDialog to screens folder.
TODO (not important) use Select comp for Gender.
TODO (not important) add benefit's icon
TODO (not important) change select text color
TODO (not important) fixe headerRightBlock social media marge-top 
TODO (not important) change logo color in perksFooter  components
TODO (not important) change isFNEmpty to isFnValid and do that to all the others fields
TODO (not important) let the loading icon moves in login in the header
TODO (not important)  find another way to display perksFooter
TODO (not important) add screens titles
TODO (not important) improve loading icon in loginScreen and also in loginDialog.
TODO (not important) redirect the user where he/she was after login.
TODO (not important) add title to the pages 
TODO (not important) change the logo in the title.
TODO (not important) fix loading images
TODO (not important) try to make the following code in LoginScreen.jsx more clear:
TODO (not important) let user sign up for newsletters 
TODO (not important) send message to the users that sign up for newsletters
TODO (NOT important) create route in backend for sending icons in quickNav component.
TODO (not important) change "product top deal" to "products".
TODO (not important) change the deal icon in product screen
TODO (not important) fixe select hover in productScreen and close the select when click on any where else.
TODO (not important) find how to get favors from the specific item.
TODO (not important) add two price instead price and priceString. 
TODO (not important) try to find another name and way to handle discount in buyingOption.
TODO (not important) STORE  topDeal in local storage.
TODO (not important) make stor-by and filter-by and start-filter individual
TODO (not important) chang range slider style like the one in MuscleAndStrung web in reveiw component.
TODO (not important) when the user enter his email then click on forgot password get his email make it easy for him cause he don't need to enter his email twice.
TODO (not important) when the user selected a favor in reviewingScreen check the selected favor from the list.
TODO (not important) ADD maxPages in userReview like the following code : data-pageno="1"
TODO (not important) ADD PageNo in userReview like the following code : data-maxpages="74"
TODO (not important) find way to handle rating attribute between Reviewing and RatingBox comps 
TODO (not important) change the name productOne to productDetails in redux store.
TODO (not important) clean all the url i mean use data option to send data 
TODO (not important) understand the following code:
TODO (not important but annoying for the user) fix when the user swipe in swiperSection and get at the last product don't let them click on the product by mistake.
TODO (not important) make the code in ProductAside more better from line 460 to 488
TODO (not important) when the user click on "write review" button in product screen first don't let the user open new window and don't let the user click on "write review" to write review
TODO (not important) learn what for attribute means and the following code:
TODO (not important) let the user visit http://localhost:3000/store/customer/account/logoutSuccess/ only when a user logout.
TODO (not important) add m&s logo in perksFooter
TODO (not important) make the footer more prefect almost like the origin website
TODO (not important) change the recommend swiper in productScreen
TODO (not important) when the user move to productScreen show him/her the state of the page
TODO (not important) make my database design better.
TODO (not important) learn how to use ESLint
TODO (not important) make your own https://www.w3schools.com/css/tryit.asp?filename=trycss3_flexbox_image_gallery
TODO (not important) make your own https://www.w3schools.com/css/tryit.asp?filename=trycss3_flexbox_website2
TODO (NOT important) let the user sees his review, make the user review first one.
TODO (not important) add multi category feature.
TODO (not important) add limit for adding product's features. 
TODO (not important) update home screen design.
TODO (not important) add autoCompletion functionality when inputting in search input
TODO (NOT important) pass , isOptionsBtn, showingTitle in better way 
TODO (NOT important) fix responsive for small mobile in search screen
TODO (not important) clean note.tex file
TODO (not important) clean note.tex file
TODO (not important) add x button when showing message let the user close it. 
TODO (not important) learn how to write README file in add it to my repository.

TODO (not important) add commit functionality to userReview component.
TODO (not important) when the user click on submenu close the submenu for ex: when the user click on "store" in header.
TODO (not important) learning more about styled-components
TODO (not important) find out why the following code in App.js doesn't work
TODO   learning how to add TRENDING products and then impalement in storeScreen this TRENDING section
      note: change the second top deal section to trending 
      note: maybe this is depended on the more review products.
