TODO   make all the element in product in center in "searchScreen" and don't show view more btn if there not more products
TODO   fix the select style in admin product screen
TODO   create buyingOption modal 
TODO   add popup window for add buying Options
TODO   fix Cast to ObjectId failed for value "null" at path "user" for model "cart" when the user not logged in.
TODO   add the right data in brandScreen 
TODO   (after Verified functionality) change totalVerified value in getAllReviews store when the user add or remove his/her review and he/she verified buyer
TODO fix Cast to ObjectId failed for value "undefined" at path 
      "user" for model "cart" when the user logged out

TODO imporve your search by add query in you url like the following :https://www.muscleandstrength.com/store/search?q=Dymatize+ISO100
DONE
--------------------------------------------
- add Deals attribute product modal than add them to homeScreen 
       at deal section bring up those product that has deal.
       commit -m "created Deal modal and connected it with product modal, fetched products with deals in 
       storeScreen"
- learning how to add this week top deal and then impalement in storeScreen this week top deal section
      commit -m "impaled [this week top deal] api and used in frontend"

-bring up the product in to rated product section from backend 
      note: it's seems easy so try to study the orange website and see how they do it.
      commit -m "impaled [get rated products] api and used in frontend"

-   learn how to logout the user after sometime of login and 
            then add that functionality
      commit -m "added <logout the user after one week> functionality"

- store activeIndex in localStorage. (in adminScreen)
      commit -m "storing activeIndex <last time the user select item in sidebar in admin screen> in localStorage"

- learn how to add youtube video and then do it in some 
      productScreen that have youtube video dah.

- improve the search form case sensitive to not.

-  (it's actually a note) if the product has different size, 
      we need to add each size and when
      clicking one of the size to view the product, show the 
      user all the size available of that product.
      https://www.muscleandstrength.com/store/search?q=Dymatize+ISO100
      study Dymatize ISO100 as example
      commit -m "created new api for get one product, used supProduct in productScreen in buying options"

-   make button global styled component and flexible 
      (hasLoader props).
      commit -m "created global Button Component"

- clean up my database delete unwanted documents.
      commit -m "cleaned up my database from unwanted documents"
-  tell a user when he/she adding product to cart without 
selecting flavor and quantity (just high light the selector)
      commit -m "showed error to the user when adding product to cart without selecting flavor"

-   fix view product in searchScreen and also when clicking on the image and title.
      commit -m "fixed product style in searchScreen and when clicking one a image , a deal or a view product Btn redirect the user to the productScreen."
--------------------------------------------
Cannot do it
